---
title: "Accuracy graphics for Deception Test Case"
output: html_document
params:
  outDir: "."
  trDat: trDat
  target: target
  target2: target2
  tid: tid
  rseed: NA
  infiles: infiles
  mmu: mmu
  mname: mname
  field_transect: field_transect
  
---

## This should be setup in a 4 deep loop
1. i iterations of models. I don't think we need to worry about point reduction. We are using the test transect metrics. 
        Effect of tp balancing, raw, smote .25/downsample 75, smote .5/down 50, smote .75/down 25, smote 1/down50
2. j iterations of BGC
3. k iterations of Train/Test slices leave one out (build 4 test 1. Further test of build 3 test 2, build 2 test 3, and build 1 test 4  for the ESSFmc and SBSmc2 only once inner loop optimization has occurred)
4. for each iteration build cv model and predict test -> return accuracy metrics 
Prepare directories

```{r setup, include=FALSE}

library(data.table)
library(scales)
library(cowplot)
library(caret)
library(sf)
library(ranger)
library(tidyverse)
library(fasterize)
library(stringr)
library(dplyr)
library(raster)
library(terra)
library(readxl)
library(stars)
library(stringr)
library(foreach)
library(tidymodels)
library(themis)
library(vip)
require(stringi)
require(R.utils)
library(data.table)
library(knitr)
library(themis)
library(ggplot2)
library(gridExtra)
library(janitor)
require(magicfor) 
require(ggpubr)
require(ggthemes)
require(viridis)
require(viridisLite)
require(philentropy)
require(formattable)
require(utils)
#devtools::install_github("tidymodels/tune")
#devtools::install_github("tidymodels/parsnip")


```

```{r session setup, tidy = TRUE, warning=FALSE}

AOI <- "Deception"
#AOI <- "BoundaryTSA"
# set up file structure
AOI_dir <- file.path(".", paste0(AOI,"_AOI"))
cov_dir <- file.path(AOI_dir, "1_map_inputs", "covariates")
shapes_dir <- file.path(AOI_dir, "0_raw_inputs", "base_layers")
input_pnts_dir <- file.path(AOI_dir, "1_map_inputs", "trainingData")
out_dir <- file.path(AOI_dir, "3_maps_analysis","models")
results_dir <- file.path(AOI_dir, "results")
paper_dir <- file.path("./PEM_standards_manuscripts/models/paper_all_var")
# read in temp functions
#source(here::here('_functions', 'model_gen.R'))
#source(here::here('_functions', 'point_subsample.R'))
#source(here::here('_functions', 'predict_map.R'))
source(here::here('_functions', 'model_gen_tidy.R'))
source(here::here('_functions', 'acc_metrix_WHM.R'))
source(here::here('_functions', 'doc_theme_pem.R'))

```

```{r create comparative boxplots, echo = FALSE, eval = TRUE}
#### best overall balanced models from training point balancing work
### import best model accuracy data

####___________________________comparison for rebalanced vs raw (with no extra points)
acc1 <- fread(file.path(paper_dir, "ESSFmc", "noextra_balancing", "acc_ds_60_sm_0.5.csv")) %>% data.frame %>% replace(is.na(.), 0) %>%
  mutate(balance = "rebalanced")
acc2 <- fread(file.path(paper_dir, "ESSFmcw", "noextra_balancing", "acc_ds_20_sm_0.5.csv")) %>% data.frame %>% replace(is.na(.), 0)%>%
  mutate(balance = "rebalanced")
acc3 <- fread(file.path(paper_dir, "SBSmc2", "noextra_balancing", "acc_ds_40_sm_0.8.csv")) %>% data.frame %>% replace(is.na(.), 0) %>%
  mutate(balance = "rebalanced")


#
acc4 <- fread(file.path(paper_dir, "ESSFmc", "noextra_balancing", "acc_raw.csv")) %>% data.frame %>% replace(is.na(.), 0) %>%
  mutate(balance = "raw")
acc5 <- fread(file.path(paper_dir, "ESSFmcw", "noextra_balancing", "acc_raw.csv")) %>% data.frame %>% replace(is.na(.), 0) %>%
  mutate(balance = "raw")
acc6 <- fread(file.path(paper_dir, "SBSmc2", "noextra_balancing", "acc_raw.csv")) %>% data.frame %>% replace(is.na(.), 0) %>%
  mutate(balance = "raw")

acc_all <- rbind(acc4, acc5, acc6, acc1, acc2, acc3)

####comparison for rebalanced vs raw (with extrapoints) 
# acc1 <- fread(file.path(paper_dir, "ESSFmc", "extrapts_balancing", "acc_ds_30_sm_0.8.csv")) %>% data.frame %>% replace(is.na(.), 0) %>% 
#  mutate(balance = "rebalanced")
# acc2 <- fread(file.path(paper_dir, "ESSFmcw", "extrapts_balancing", "acc_ds_50_sm_0.5.csv")) %>% data.frame %>% replace(is.na(.), 0) %>% 
#  mutate(balance = "rebalanced")
# acc3 <- fread(file.path(paper_dir, "SBSmc2", "extrapts_balancing", "acc_ds_30_sm_0.4.csv")) %>% data.frame %>% replace(is.na(.), 0) %>% 
#  mutate(balance = "rebalanced")
# 
# acc4 <- fread(file.path(paper_dir, "ESSFmc", "extrapts_balancing", "acc_raw.csv")) %>% data.frame %>% replace(is.na(.), 0) %>% 
#   mutate(balance = "raw")
# acc5 <- fread(file.path(paper_dir, "ESSFmcw", "extrapts_balancing", "acc_raw.csv")) %>% data.frame %>% replace(is.na(.), 0) %>% 
#    mutate(balance = "raw")
# acc6 <- fread(file.path(paper_dir, "SBSmc2", "extrapts_balancing", "acc_raw.csv")) %>% data.frame %>% replace(is.na(.), 0) %>% 
#    mutate(balance = "raw")
# 
# 
# acc_all <- rbind(acc4, acc5, acc6, acc1, acc2, acc3)


####___________________________comparison for standard points and extrapoints

# acc1 <- fread(file.path(paper_dir, "ESSFmc", "extrapts_balancing", "acc_raw.csv")) %>% data.frame %>% replace(is.na(.), 0) %>% dplyr::filter(acc_type == "test_estimate")
# acc1$balance = "extra"
# 
# acc2 <- fread(file.path(paper_dir, "ESSFmcw", "extrapts_balancing", "acc_raw.csv")) %>% data.frame %>% replace(is.na(.), 0) %>% dplyr::filter(acc_type == "test_estimate")
# acc2$balance = "extra"
# acc3 <- fread(file.path(paper_dir, "SBSmc2", "extrapts_balancing", "acc_raw.csv")) %>% data.frame %>% replace(is.na(.), 0) %>% dplyr::filter(acc_type == "test_estimate")
# acc3$balance = "extra"
# acc_all <- rbind(acc1, acc2, acc3)
# 
# acc4 <- fread("./Deception_AOI/3_maps_analysis/models/forest_non_forest/for_nfor_bgc/999/ESSFmc/acc_raw.csv") %>% data.frame %>% replace(is.na(.), 0) %>% dplyr::filter(acc_type == "test_estimate")
# acc4$balance = "balanced"
# 
# acc5 <- fread("./Deception_AOI/3_maps_analysis/models/forest_non_forest/for_nfor_bgc/999/ESSFmcw/acc_raw.csv") %>% data.frame %>% replace(is.na(.), 0) %>% filter(acc_type == "test_estimate")
# acc5$balance = "balanced"
# acc6 <- fread("./Deception_AOI/3_maps_analysis/models/forest_non_forest/for_nfor_bgc/999/SBSmc2/acc_raw.csv") %>% data.frame %>% replace(is.na(.), 0) %>% filter(acc_type == "test_estimate")
# acc6$balance = "balanced"
# 
# acc_all <- rbind(acc4, acc5, acc6, acc, acc2, acc3)

acc_all <- rbind(acc4, acc5, acc6, acc1, acc2, acc3)
noi <-  names(acc_all)[str_detect(names(acc_all),"_theta")]

 
   acc_all <- acc_all %>%
     mutate(bgc = factor(bgc), slice = factor(slice),  balance = factor(balance)) %>% 
     dplyr::select(balance, bgc, slice, acc, kap, oob, noi)
   
noi2 <-  names(acc_all)[str_detect(names(acc_all),"_w")]   
     
acc_all <-    acc_all  %>% 
     dplyr::select(-noi2) %>% 
     mutate(across(where(is.numeric), ~ . *100)) %>% distinct() %>% 
     mutate(OOB_inv = (100-oob),
            MLaccuracy = acc,
            #mcc = mcc *100,
            kappa = kap) %>% 
     dplyr::select(-oob, -acc, -kap) 

    acc_all2 <- acc_all %>% 
   pivot_longer(cols = where(is.numeric), names_to = "accuracy_type", values_to = "value") %>%
     distinct() %>% 
  mutate(type = case_when(
       accuracy_type %in% c("MLaccuracy", "OOB_inv",  "kappa", "mcc") ~ "0_machine",
      str_detect(accuracy_type, "aspat_pa_") ~ "4_aspatial",
      str_detect(accuracy_type, "^spat_p_") ~ "1_primary",
       str_detect(accuracy_type, "^spat_pa_") ~ "2_p+alternate",
       str_detect(accuracy_type, "^spat_paf_") ~ "3_fuzzy_p+a")) %>% 
     filter(!is.na(type)) %>% filter(!accuracy_type == "slice") %>% 
     mutate(accuracy_type = str_replace(accuracy_type, "theta1", "theta 1"),
       accuracy_type = str_replace(accuracy_type, "aspat_pa_theta", "\u0398 "),
       accuracy_type = str_replace(accuracy_type, "spat_paf_theta", "\u0398 "),
       accuracy_type = str_replace(accuracy_type, "spat_pa_theta", "\u0398 "),
       accuracy_type = str_replace(accuracy_type, "spat_p_theta", "\u0398 "))
    #acc_all2 <- acc_all2 %>% dplyr::filter(bgc == "SBSmc2", balance == "rebalanced") %>% mutate(accuracy_type2 = as.factor(accuracy_type)) %>% droplevels()
    
  ###Create ggplot graphic
           overall_acc <- ggplot(aes(y = value, x = accuracy_type, fill = balance ), data = acc_all2 ) + # fill = accuracy_type2
     geom_boxplot() +
     scale_fill_brewer(type = "qual") +
     facet_grid(bgc ~ type, labeller = labeller(type = 
                                             c("0_machine" = "machine",
                                               "1_primary" = "primary",
                                               "2_p+alternate" = "alternate",
                                               "3_fuzzy_p+a" = "fuzzy",
                                               "4_aspatial" = "proportional (p+a)")), scales = "free_x")+
     #facet_wrap(~acc_type)+
     #geom_jitter(position=position_jitter(width=.1), colour = "grey", alpha = 0.8) + 
     geom_hline(yintercept = 65,linetype ="dashed", color = "black") + 
      theme_pem_facet() +
       #scale_fill_manual(values=c("grey90", "grey70", "grey50"))+
     theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") +
     xlab("Metric") + ylab("Accuracy") + 
     ylim(25, 100)

   
   overall_acc
   
   finalise_facet_plot(overall_acc, "./PEM_standards_manuscripts/outputs/accuracy_raw_vs_balance_no_extras_25limit.png", width_pixels=480,
                          height_pixels=480)
   
      #finalise_facet_plot(overall_acc, "./PEM_standards_manuscripts/outputs/accuracy_for_ppt.png", width_pixels=480,                        height_pixels=480)
```


```{r old, echo = FALSE, eval = TRUE}
# acc_tab <- acc_theta_raw2 %>%  dplyr::select(-slice, -type) %>% mutate(accuracy_type = factor(accuracy_type)) %>%   
   #   group_by(bgc, balance, accuracy_type) %>%
   #   summarise(mean = mean(value))
  #   group_by(bgc, balance, slice) #%>%
  #    #dplyr::summarise(across(everything(), ~ mean(., is.na(.), 0)))
  # 
  # 
  # acc_theta <- acc_all %>%
  #   group_by(bgc, balance,slice) %>%
  #   mutate(no.classes = length(unique(target))) %>%
  #   ungroup() %>% 
  #   mutate(primary_theta.5 = spat_p_theta.5*100,
  #          p_alternate_theta.5 = spat_pa_theta.5*100,
  #          p_a_fuzzy_theta.5 = spat_paf_theta.5*100,
  #          primary_theta0 = spat_p_theta0*100,
  #          p_alternate_theta0 = spat_pa_theta0*100,
  #          p_a_fuzzy_theta0 = spat_paf_theta0*100,
  #          primary_theta.1 = spat_p_theta1*100,
  #          p_alternate_theta.1 = spat_pa_theta1*100,
  #          p_a_fuzzy_theta.1 = spat_paf_theta1*100,
  #           #aspatial_theta.5 = theta_wt *  (min(pred.tot,trans.tot)/trans.tot),
  #           #aspatial_theta0 = raw_wt *  (min(pred.tot,trans.tot)/trans.tot),
  #         # aspatial_theta.1 = mean_wt *  (min(pred.tot,trans.tot)/trans.tot),
  #           aspatial_fpa_theta.5 = aspat_p_theta.5*100,
  #           aspatial_fpa_theta0 = aspat_fpa_theta0*100,
  #          aspatial_fpa_theta.1 = aspat_fpa_theta1*100)
  # 
  # 
  # noi <-  names(acc_theta)[str_detect(names(acc_theta),"_theta")]
  # 
  #  acc_theta_target <- acc_theta %>%
  #   dplyr::select(bgc, target, balance,slice, all_of(noi))
  # 
  # acc_theta <- acc_theta %>%
  #   dplyr::select(bgc, balance,slice, all_of(noi))
  # 
  # acc_theta[is.na(acc_theta)] <- 0
  # 
  #  acc_theta_raw <- acc_theta %>%
  #    mutate(bgc = factor(bgc), slice = factor(slice), balance = factor(balance)) %>% 
  #   group_by(bgc, balance, slice) #%>%
  #    #dplyr::summarise(across(everything(), ~ mean(., is.na(.), 0)))
  #  
  # # acc_theta_raw <- acc_theta_raw %>%
  # #   dplyr::select(slice, all_of(noi)) %>% distinct()
  # #    
  #  ML_acc <- acc_all %>% dplyr::select(bgc, balance, slice, acc,  oob, kap) %>% 
  #    mutate(OOB_inv = (1-oob)*100,
  #           MLaccuracy = acc *100,
  #           #mcc = mcc *100,
  #           kappa = kap * 100) %>% 
  #    dplyr::select(-oob, acc) %>% distinct() #%>% filter(bgc == "SBSmc2", balance == "rebalanced")
  #  
  #  acc_theta_raw2 <- merge(acc_theta_raw, ML_acc, by.x = c("bgc" ,"balance", "slice")) %>% mutate(slice = factor(slice), bgc = factor(bgc), balance = factor(balance)) %>% 
  #  pivot_longer(cols = where(is.numeric), names_to = "accuracy_type", values_to = "value") %>%
  #    distinct() %>% 
  #    mutate(type = case_when(
  #      accuracy_type %in% c("MLaccuracy", "OOB_inv",  "kappa", "mcc") ~ "0_machine",
  #     str_detect(accuracy_type, "aspatial") ~ "4_aspatial",
  #     str_detect(accuracy_type, "primary") ~ "1_primary",
  #      str_detect(accuracy_type, "alternate") ~ "2_p+alternate",
  #      str_detect(accuracy_type, "fuzzy") ~ "3_fuzzy_p+a")) %>% 
  #    filter(!is.na(type)) %>% filter(!accuracy_type == "slice") %>% 
  #    mutate(accuracy_type = str_replace(accuracy_type, "theta.1", "theta 1"),
  #      accuracy_type = str_replace(accuracy_type, "primary_theta", "\u0398 "),
  #      accuracy_type = str_replace(accuracy_type, "p_alternate_theta", "\u0398 "),
  #      accuracy_type = str_replace(accuracy_type, "p_a_fuzzy_theta", "\u0398 "),
  #      accuracy_type = str_replace(accuracy_type, "aspatial_fpa_theta", "\u0398 "))
  #  #   )) %>%
  #  
   # 
   #   overall_acc <- ggplot(aes(y = value, x = accuracy_type, fill = balance), data = acc_theta_raw2) + #fill = accuracy_type
   #   geom_boxplot() +
   #   scale_fill_brewer(type = "qual") +
   #   facet_grid(bgc ~ type, labeller = labeller(type = 
   #                                           c("0_machine" = "machine",
   #                                             "1_primary" = "primary",
   #                                             "2_p+alternate" = "alternate",
   #                                             "3_fuzzy_p+a" = "fuzzy",
   #                                             "4_aspatial" = "aspatial")), scales = "free_x")+
   #   #facet_wrap(~acc_type)+
   #   #geom_jitter(position=position_jitter(width=.1), colour = "grey", alpha = 0.8) + 
   #   geom_hline(yintercept = 65,linetype ="dashed", color = "black") + 
   #    theme_pem_facet() +
   #     scale_fill_manual(values=c("grey90", "grey70", "grey50"))+
   #   theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") +
   #   xlab("Metric") + ylab("Accuracy") + 
   #   ylim(-0.05, 100)
   # 
   # 
   # overall_acc
   # 
   # finalise_facet_plot(overall_acc, "./PEM_standards_manuscripts/outputs/accuracy_raw_vs_balance_no_extras.png", width_pixels=480,
   #                        height_pixels=480)
   # 
   # acc_tab <- acc_theta_raw2 %>%  dplyr::select(-slice, -type) %>% mutate(accuracy_type = factor(accuracy_type)) %>%   
   #   group_by(bgc, balance, accuracy_type) %>%
   #   summarise(mean = mean(value))

#ggsave()
```
Run this to identify mapunits with low accuracy and so extra points should be acquired for that test.

```{r same but by individual mapunit rather than theta for single accuracy run}
acc_all <- fread("./Deception_AOI/3_maps_analysis/models/forest_non_forest/for_nfor_bgc/999/ESSFmcw/extrapts/acc_raw.csv") %>%   dplyr::select(unique(colnames(.)))%>% replace(is.na(.), 0) %>% dplyr::filter(acc_type == "test_estimate")

acc_all <- acc_all %>%
    dplyr::select(bgc,target,slice, transect_no,target, spat_fpa_unit_pos,aspat_fpa_unit_pos)
                  #spat_p_unit_pos, spat_pa_unit_pos,   aspat_p_unit_pos, aspat_pa_unit_pos, )

  acc_theta_target <- acc_all %>%
    group_by(bgc, slice, target) %>%
    mutate(no.classes = length(unique(target))) %>%
    ungroup()
  
 # acc_theta_target[is.na( acc_theta_target)] <- 0
  
   acc_theta_raw <- acc_theta_target  %>% 
     mutate(bgc = factor(bgc), slice = factor(slice), target = factor(target)) %>% 
    group_by(bgc, slice, target) %>%
     dplyr::summarise(across(everything(), ~ sum(., is.na(.), 0)))
   

   acc_theta_raw2 <- acc_theta_raw %>% 
   pivot_longer(cols = where(is.numeric), names_to = "accuracy_type", values_to = "value") %>%
     distinct() %>% 
    filter(!accuracy_type == "no.classes") %>% filter(!accuracy_type == "transect_no")

 
     overall_acc <- ggplot(aes(y = value, x = target, fill = accuracy_type), data = acc_theta_raw2) + 
     geom_boxplot() +
     scale_fill_brewer(type = "qual") +
     # facet_grid(bgc ~ type, labeller = labeller(type = 
     #                                         c("0_machine" = "machine",
     #                                           "1_primary" = "primary",
     #                                           "2_p+alternate" = "alternate",
     #                                           "3_fuzzy_p+a" = "fuzzy",
     #                                           "4_aspatial" = "transect")), scales = "free_x")+
     #facet_wrap(~acc_type)+
     #geom_jitter(position=position_jitter(width=.1), colour = "grey", alpha = 0.8) + 
     geom_hline(yintercept = .65,linetype ="dashed", color = "black") + 
      theme_pem_facet() +
       #scale_fill_manual(values=c("grey90", "grey50"))+
     theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") +
     xlab("Metric") + ylab("Accuracy") + 
     ylim(-0.05, 1)

   
   overall_acc
   
   finalise_facet_plot(overall_acc, "./Deception_AOI/results/UnitAccuracyMetrics_boxplot.png", width_pixels=480,
                          height_pixels=480)
   
   # acc_tab <- acc_theta_raw2 %>%  dplyr::select(-slice, -type) %>% mutate(accuracy_type = factor(accuracy_type)) %>%   
   #   group_by(bgc, balance, accuracy_type) %>%
   #   summarise(mean = mean(value))
```

```{r compare balancing}

# ##predictions from raw data model
#   acc_raw <- fread("H:/BEC_DevExchange_Work/Deception_AOI/3_maps_analysis/models/forest/fore_mu_bgc/87/SBSmc2/acc_raw.csv") %>% replace(is.na(.), 0) %>% filter(acc_type == "test_estimate")
# acc_raw$balance = "0_raw"
#   acc_max <- fread("H:/BEC_DevExchange_Work/Deception_AOI/3_maps_analysis/models/forest/fore_mu_bgc/87/SBSmc2/acc_ds_80_sm_0.2.csv") %>% replace(is.na(.), 0) %>% filter(acc_type == "test_estimate")
#   acc_max$balance = "1_max"
#   acc_avr <- fread("H:/BEC_DevExchange_Work/Deception_AOI/3_maps_analysis/models/forest/fore_mu_bgc/87/SBSmc2/acc_ds_15_sm_0.5.csv") %>% replace(is.na(.), 0) %>% filter(acc_type == "test_estimate")
#   acc_avr$balance = "2_mean"
#   
#   acc_bal <- rbind(acc_raw, acc_max, acc_avr)
#     acc_bal$bgc = "SBSmc2"
#      acc_bal <-   acc_bal %>%  dplyr::select(bgc, balance, slice, target, spat_fpa.x, trans.tot, trans.sum) %>% rename("spat_fpa" = "spat_fpa.x")
# 
#   
#     acc_raw <- fread("H:/BEC_DevExchange_Work/Deception_AOI/3_maps_analysis/models/forest/fore_mu_bgc/87/ESSFmc/acc_raw.csv") %>% replace(is.na(.), 0) %>% filter(acc_type == "test_estimate")
# acc_raw$balance = "0_raw"
#   acc_max <- fread("H:/BEC_DevExchange_Work/Deception_AOI/3_maps_analysis/models/forest/fore_mu_bgc/87/ESSFmc/acc_ds_40_sm_0.6.csv") %>% replace(is.na(.), 0) %>% filter(acc_type == "test_estimate")
#   acc_max$balance = "1_max"
#   acc_avr <- fread("H:/BEC_DevExchange_Work/Deception_AOI/3_maps_analysis/models/forest/fore_mu_bgc/87/ESSFmc/acc_ds_15_sm_0.2.csv") %>% replace(is.na(.), 0) %>% filter(acc_type == "test_estimate")
#   acc_avr$balance = "2_mean"
#   
#   acc_bal2 <- rbind(acc_raw, acc_max, acc_avr)
#   acc_bal2$bgc = "ESSFmc"
#   
#    acc_bal2 <-  acc_bal2 %>%  dplyr::select(bgc, balance, slice, target, spat_fpa, trans.tot, trans.sum)
#   
#     acc_raw <- fread("H:/BEC_DevExchange_Work/Deception_AOI/3_maps_analysis/models/forest/fore_mu_bgc/87/ESSFmcw/acc_raw.csv") %>% replace(is.na(.), 0) %>% filter(acc_type == "test_estimate")
# acc_raw$balance = "0_raw"
#   acc_max <- fread("H:/BEC_DevExchange_Work/Deception_AOI/3_maps_analysis/models/forest/fore_mu_bgc/87/ESSFmcw/acc_ds_40_sm_0.8.csv") %>% replace(is.na(.), 0) %>% filter(acc_type == "test_estimate")
#   acc_max$balance = "1_max"
#   acc_avr <- fread("H:/BEC_DevExchange_Work/Deception_AOI/3_maps_analysis/models/forest/fore_mu_bgc/87/ESSFmcw/acc_ds_15_sm_0.6.csv") %>% replace(is.na(.), 0) %>% filter(acc_type == "test_estimate")
#   acc_avr$balance = "2_mean"
#   
#   acc_bal3 <- rbind(acc_raw, acc_max, acc_avr)
#   acc_bal3$bgc = "ESSFmcw"
#   
#    acc_bal3 <-  acc_bal3 %>%  dplyr::select(bgc, balance, slice, target, spat_fpa, trans.tot, trans.sum)
#   acc_bal_all <- rbind(acc_bal, acc_bal2, acc_bal3)
#   
#   acc_theta <- acc_bal_all %>%
#     group_by(bgc, balance, slice) %>%
#     mutate(no.classes = length(unique(target))) %>%
#     ungroup()
#   
#   # calculate the theta_spat_p
#   theta = 0.5
#   acc_theta <- acc_theta %>%
#     rowwise() %>%
#     mutate(theta_wt = (theta * (1/no.classes) + (1-theta) * (trans.tot/trans.sum))*100) %>%
#     mutate(raw_wt = (trans.tot/trans.sum)*100) %>%
#     mutate(mean_wt = (1/no.classes)*100) %>%
#     mutate(theta.5 = theta_wt *  (spat_fpa/trans.tot),
#            theta0 = raw_wt *  (spat_fpa/trans.tot),
#            theta.1 = mean_wt *  (spat_fpa/trans.tot))
# 
#   noi <-  names(acc_theta)[str_detect(names(acc_theta),"theta")]
#   
#   acc_theta <- acc_theta %>%
#     dplyr::select(bgc, balance, slice, all_of(noi))# %>% distinct()
#   
#   
#    acc_theta_raw <- acc_theta %>%
#     group_by(bgc, balance, slice) %>%
#      summarise(across(everything(), ~ sum(., is.na(.), 0)))
#    
#    acc_theta_raw2 <- acc_theta_raw %>% mutate(slice = factor(slice), bgc = factor(bgc), balance = factor(balance) ) %>% 
#    pivot_longer(cols = where(is.numeric), names_to = "accuracy_type", values_to = "value") %>%
#      distinct() %>% 
#      mutate(type = factor(accuracy_type)) %>% 
#      filter(!type == "theta_wt")# %>% 
#      #mutate(accuracy_type = str_replace(accuracy_type, 'theta', '$/theta'))
#             
#    overall_acc <- ggplot(aes(y = value, x = type), data = acc_theta_raw2) + 
#      geom_boxplot() +
#      scale_fill_brewer(type = "qual") +
#      facet_grid(bgc ~ balance, labeller = labeller(balance = 
#                                              c("0_raw" = "raw",
#                                                "1_max" = "theta = 0 optimized",
#                                                "2_mean" = "theta = 1 optimized")), scales = "free_x")+
#      #facet_wrap(~acc_type)+
#      #geom_jitter(position=position_jitter(width=.1), colour = "grey", alpha = 0.8) + 
#      geom_hline(yintercept = 65,linetype ="dashed", color = "black") + 
#      #ggtitle("Map accuracy metrics by biogeoclimatic units from raw training data") + 
#      theme_pem_facet() +
#      theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#      xlab("Mapunit") + ylab("Accuracy") + 
#      ylim(-0.05, 100)
# 
#    
#    overall_acc
#    
#    finalise_facet_plot(overall_acc, "./Deception_AOI/results/BalancedAccuracyMetrics_boxplot.png", width_pixels=640,
#                           height_pixels=450)

```


## Accuracy per mapunit

We can compare map unit accuracy levels to assess under or acceptable performance per map units. 

```{r generate accuracy by mapunit, echo = FALSE, eval = TRUE}

# mapunit_tot <- bsRes %>% 
#   dplyr::filter(acc_type == "test_estimate") %>%
#   group_by(slice, target, acc_type) %>%
#   dplyr::select(mu_spat_p_acc, mu_spat_fp_acc, mu_spat_pa_acc, mu_spat_fpa_acc, unit_pos)%>%
#   rowwise() %>%
#   # mutate(spat_p_tot = (spat_p/trans.tot) *100,
#   #        spat_pa_tot = (spat_pa/trans.tot) *100,
#   #        spat_fp_tot = (spat_fp/trans.tot)*100,
#   #        spat_fpa_tot = (spat_fpa/trans.tot)*100,
#   #        aspat_p = unit_pos *100) %>%
#   # dplyr::select(slice, target, spat_p_tot,
#   #               spat_pa_tot, spat_fp_tot, spat_fpa_tot, aspat_p) %>%
#   pivot_longer(., cols = where(is.numeric), names_to = "type") %>% 
#    filter(!is.na(type)) %>% filter(!type == "slice")
#          
# mapunit_tot$type <- as.factor(mapunit_tot$type) %>% 
#   factor(levels = c('mu_spat_p_acc', 'mu_spat_pa_acc','mu_spat_fp_acc',  'mu_spat_fpa_acc', 'unit_pos'))
# 
# MU_accuracy <- ggplot(aes(y = value, x = target, fill = type), data = mapunit_tot) + 
#    geom_boxplot() + 
#    #facet_wrap(~acc_type) + 
#    geom_hline(yintercept = 65,linetype ="dashed", color = "red") + 
#    ggtitle(paste0("Test accuracy per mapunit_", bgcs)) + 
#    theme(axis.text.x = element_text(angle = 90)) +
#    xlab("Mapunit") + ylab("Accuracy") + 
#    ylim(-0.01, 1)+
#    scale_fill_discrete(name = "Accuracy Metric", labels = c("Primary", "Primary/Alt", "Fuzzy Primary", "Fuzzy Primary/Alt", "Aspatial Unit Positive"))+
#   geom_hline(yintercept = .65, colour = "red", linetype = "dashed")+
#   theme_light()
# 
# MU_accuracy 
# 
# ggsave(paste0("./Deception_AOI/results/", bgcs, "_MU_AccuracyMetrics_boxplot_1.jpg"))
# 
# ```
# ```{r read in existing graphic files and arrange}
# rl = lapply(sprintf("my_viz%i.png", 1:4), png::readPNG)
# gl = lapply(rl, grid::rasterGrob)
# gridExtra::grid.arrange(grobs=gl)
```



