---
title: "05a_Clean Raster PEM"
author: "G. Perkins & W. MacKenzie"
date: "06/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(dplyr)
library(readxl)
library(stringr)
library(raster)
library(stars)
require(data.table)
#install.packages("pemgeneratr")

```

This script will merge different modelled maps together and do some simplification to create a final raster map
1. Replace cutblocks with a forest only map
2. Add in a water layer
3. Merge a non-forest model into a forest model

May sieve a raster map to remove individual or small cluster types

```{r set up folders, echo = FALSE}

AOI <- "Deception"

#AOI <- "DateCreek"


#read in functions: 
source(here::here('_functions', 'predict_map_tidy.R'))
## folder with BGC random forest models
outDir <- "../PEM_standards_manuscripts/models/paper_ss_all_var/rF_models"

# set up file structure
AOI_dir <- file.path("..", paste0(AOI,"_AOI"))
cov_dir <- file.path(AOI_dir, "1_map_inputs", "covariates")
shapes_dir <- file.path(AOI_dir, "0_raw_inputs", "base_layers")
out_dir <- file.path(AOI_dir, "3_maps_analysis","models")
out_dir <- file.path(AOI_dir, "models")
input_pnts_dir <- file.path(AOI_dir, "1_map_inputs", "trainingData", "att_5m")
bec_shp <- st_read(file.path(shapes_dir, "bec.gpkg"), quiet = TRUE)
  
# read in map and model keys
map.key <-  read.csv("../PEM_standards_manuscripts/_MapUnitLegend/Deception_MapUnitLegend.csv", 
                       stringsAsFactor = FALSE)
#map.key <- read.csv(paste0(AOI_dir, "/_MapUnitLegend/", AOI, "_MapUnitLegend.csv"))

model_param <- file.path("../PEM_standards_manuscripts/_MapUnitLegend/models_WHM.xlsx")

# set up model parameters:  
mparam <- read_xlsx(model_param, "models") %>% filter(to_run == 1)
map_res <- mparam$resolution
mname <- paste0(mparam$model_name)
mrep <- mparam$model_rep

# check which catergory of model to be produced
mtype <- case_when(
  str_detect(mname, "for_nf")  ~ "forest_non_forest",
  str_detect(mname, "nf_") ~ "non_forest",
  str_detect(mname, "fore") ~ "forest"
)

# get covariates for model
mcov <- read_xlsx(model_param, "covariates", skip = 2) %>%
  filter(!!sym(mparam$covariates) == 1) %>%
  dplyr::select(covariate)


```


## Generate final AOI map by joining BGC map mosaics together

```{r combine BGC maps into single AOI map}
# Assemble the BGC's maps: 

AOI <- "Deception"
AOI <- "DateCreek"
# set up file structure
AOI_dir <- file.path("..", paste0(AOI,"_AOI"))
cov_dir <- file.path(AOI_dir, "1_map_inputs", "covariates")
shapes_dir <- file.path(AOI_dir, "0_raw_inputs", "base_layers")
out_dir <- file.path("../PEM_standards_manuscripts/models", mname, "maps")

# load bgc layer

bec_shp <- st_read(file.path(shapes_dir, "bec.gpkg"), quiet = TRUE) %>%
  mutate(MAP_LABEL = gsub(" ","",MAP_LABEL))

aoi <- st_read(file.path(shapes_dir, "AOI.gpkg"), quiet = TRUE)

# read in map and model keys
map.key  <- fread("D:/GitHub/PEM_Methods_DevX/PEM_standards_manuscripts/_MapUnitLegend/Deception_MapUnitLegend.csv")

map_dir = paste0("../PEM_standards_manuscripts/models/", mname, "/rF_models")


#folders <- as.list(c("SBSmc2")) 
folders <- as.list(c("ESSFmc", "ESSFmcw", "SBSmc2")) 

# step 1:  set up a key for the combined map (includes all the units)
rkey <- lapply(folders, function (f){
  
  keys <- read.csv(file.path(map_dir, f, "response_names.csv")) %>%
    mutate(model  = f)
})

rkey <- do.call("rbind", rkey)
rkey <- rkey %>% dplyr::mutate(map.response = seq(1:length(x)))

source("../_functions/_combine_maps.R")# create mosaic using GDAL
#rast_list <- list.files(file.path(cov_dir, res_folder), pattern = ".tif$", full.names = TRUE)
# rast_list <- list.files("D:/GitHub/PEM_Methods_DevX/PEM_standards_manuscripts/models/predicted/SBSmc2", pattern = ".tif$", full.names = TRUE)
# mosaic_rasters(gdalfile=rast_list,dst_dataset="./models/predicted/SBSmc2/SBSmc2_mapmosaic.tif",of="GTiff")

# join all the BGC specific maps together for AOI


if(length(folders) == 3) {
  
  all_key <- merge(combine_maps[[1]], combine_maps[[2]], overlap=TRUE)
  all_key <- merge(all_key, combine_maps[[3]], overlap = TRUE)

} 

# all_key <- merge(combo_map[[1]], combo_map[[2]], overlap=TRUE)
# all_key <- merge(all_key, combo_map[[3]], overlap = TRUE)
# all_key <- merge(all_key, combo_map[[4]], overlap = TRUE)
# all_key <- merge(all_key, combo_map[[5]], overlap = TRUE)
# all_key <- merge(all_key, combo_map[[6]], overlap = TRUE)
# all_key <- merge(all_key, combo_map[[7]], overlap = TRUE)

# tidy key and output maps
rkey <- rkey %>% dplyr::select(x, model, map.response)

### update raster values to match master key of all units
rkey_master <- fread("../PEM_standards_manuscripts/models/response_combo_bgcs_key_all.csv")
rkey_master2 <- left_join(rkey_master, rkey, by = 'x') %>% dplyr::select(x, map.response.x, map.response.y) %>% filter(!is.na(map.response.y)) %>%  distinct(x, .keep_all = TRUE) %>% data.frame

 raster::subs(all_key, rkey_master2, by = 'map.response.y', which = 'map.response.x', filename=file.path(out_dir, "only_forest_combo_bgcs_renumbered.tif"), overwrite = TRUE)

 ###for some reason terra does not keep all the correct response numbers - but is a lot faster
# require(terra)
# all_key_sr <- terra::rast(all_key)
# all_key_sr2 <- terra::subst(all_key_sr, rkey_master2$map.response.y, rkey_master2$map.response.x, filename=file.path(out_dir, "forest_combo_bgcs_renumbered_terra.tif"), overwrite = TRUE)

writeRaster(all_key, file.path(out_dir, "forest_combo_bgcs.tif"), overwrite = TRUE)

write.csv(rkey, file.path(out_dir, "response_combo_bgcs_key.csv"))

```

```{r clear cutblocks from all variable map }
###currently using Patching in Qgis to replace cutblock NA with the DEM only map 
cutblk <- st_read("../Deception_AOI/0_raw_inputs/base_layers/cleared_areas_atSentinelTime_updated.gpkg", quiet = TRUE)
require(fasterize)
cutblk_rast <- fasterize(aoi, all_key)
#cutblk_rast [cutblk_rast  > 0] <- NA
plot(cutblk_rast)
all_map <- raster("../PEM_standards_manuscripts/models/paper_all_var/maps/forest_combo_bgcs_all.tif")

all_key_masked <- mask(all_map,
                               mask = cutblk_rast, inverse=TRUE)

writeRaster(all_key_masked, "../PEM_standards_manuscripts/models/paper_all_var/maps/forest_combo_bgcs_masked.tif", overwrite = TRUE)

```



# generate map for forest/non_forest split 

```{r}
# temp fix 

# read in non-forest map generated at 5m accuracy
nf_f <- file.path(out_dir, "forest_non_forest/for_nfor_all/2/for_nfor_all/predicted/")
list.files(nf_f)


# generate rasters for AOI 
nf_f_map <- terra::rast(file.path(nf_f, "response.tif"))
nf_f_key <- read.csv(file.path(nf_f, "response_names.csv"))

nf_f_key <- nf_f_key %>% mutate(x = case_when(
  x == "clearcut" ~ "forest", 
  TRUE ~ as.character(.$x)))

nf_f_key
#  X         x
# 1  clearcut
# 2    forest
# 3 nonforest
# 4     water

m <- c(1,2, 1)
rclmat <- matrix(m, ncol=3, byrow=TRUE)
forest_aoi <- terra::classify(aoi, rclmat, othersNA=TRUE, include.lowest=TRUE)

m <- c(4, 1)
rclmat <- matrix(m, ncol=2, byrow=TRUE)
water_aoi <- terra::classify(aoi, rclmat, othersNA=TRUE, include.lowest=TRUE)

m <- c(3, 1)
rclmat <- matrix(m, ncol=2, byrow=TRUE)
nf_aoi <- terra::classify(aoi, rclmat, othersNA=TRUE, include.lowest=TRUE)


##aoi_poly <- aoi %>% 
#  st_as_sf(as_points = FALSE, merge = TRUE, na.rm = TRUE, use_integer = TRUE) %>%
#  st_transform(3005) %>%
#  left_join(aoi_key, by = c("response.tif" = "X"))


```


# generate the non-forest map and join to forested map

```{r}
# inorder to generate the non -forest model and join to the forested model we need to select the model of inerest : 

# define 
#- forest / non-forest mask model
#- forested model
#- non-forest model 

# AOI <- "Deception"
# #AOI <- "BoundaryTSA"
# 
# # set up file structure
# AOI_dir <- file.path(".", paste0(AOI,"_AOI"))
# out_dir <- file.path(AOI_dir, "3_maps_analysis","models")
# shapes_dir <- file.path(AOI_dir, "0_raw_inputs", "base_layers")
# 
# fnf <- file.path(out_dir, "forest_non_forest", "for_nfor", "2")
# f <- file.path(out_dir, "forest", "for_mu_bgc", "76")
# nf <- file.path(out_dir, "non_forest","nf_class","2")
# 
# # read in non-forest and forest split
# #nff_map <- stars::read_stars(file.path(fnf, "mosaic.tif"))
# nff_map  <- raster(file.path(fnf, "mosaic.tif"))
# nff_key <- read.csv(file.path(fnf, "response_names.csv"))
# 
# # read in non-forest map generated at 5m accuracy
# nf_map <- raster(file.path(nf, "mosaic.tif"))
# nf_key <- read.csv(file.path(nf, "response_names.csv"))
# 
# # crop to AOI and write out 
# #all_key <- read_stars(file.path(map_dir, "mosaic.tif"))
# #all_key <- st_crop(all_key, aoi)
# #stars::write_stars(all_key, file.path(map_dir, "mosaic1.tif")) #tile name
#        
# 
# 
# 
# aoi = st_read(file.path(shapes_dir, "AOI.gpkg")) %>%
#   st_transform(3005) 
# 
# 
# # crop to AOI and write out 
# all_key <- read_stars(file.path(nf, "mosaic.tif"))
# all_key <- st_crop(all_key, aoi)
# stars::write_stars(all_key, file.path(map_dir, "mosaic_aoi.tif")) #tile name
#     
# 
# ## Generate the non-forest mask 
# #f_mask <- nff_map < 3
# #w_mask <- nff_map == 3
# 
# nf_maks <- nff_map == 4 
# 
# nf_mask <- mask(nf_maks, as(aoi,'Spatial'))
# nf_maskpoly <- st_as_sf(nf_mask)
# 
# 
# 
# 
# 
# nf_map_masked <- mask(nf_map, nf_mask) 
# 
# writeRaster(nf_mask, file.path(nf, "nf_filter.tif"), overwrite = TRUE)



# m <- c(1,2, 1)
# rclmat <- matrix(m, ncol=3, byrow=TRUE)
# forest_aoi <- terra::classify(aoi, rclmat, othersNA=TRUE, include.lowest=TRUE)
# 
# m <- c(4, 1)
# rclmat <- matrix(m, ncol=2, byrow=TRUE)
# water_aoi <- terra::classify(aoi, rclmat, othersNA=TRUE, include.lowest=TRUE)
# 
# m <- c(3, 1)
# rclmat <- matrix(m, ncol=2, byrow=TRUE)
# nf_aoi <- terra::classify(aoi, rclmat, othersNA=TRUE, include.lowest=TRUE)







```


 
         

